msBalance

### 2019-12-19 R/msBalance.Rmd
updated main file

## Locate the Matlab source files.
Locate the source data files on your computer.
These are intended to be kept in 
This will need to be modified.

```{r}
suppressMessages(library(R.matlab))

path = "~/OneDrive - Emory University/2019 Peterson MS EMG/data"
(filePathMS = file.path(path, "AllConsolidatedData_MS.mat"))
(filePathCS = file.path(path, "AllConsolidatedData_CS.mat"))

dataMS = read.mat(filePathMS)
dataCS = read.mat(filePathCS)
```

>>>>

## Locate the Matlab source files.

```{r}
```
